A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-02-22 evaluation.tex
Add a cactus plot for QF_SLIA

\begin{table}
  \begin{center}
  \input{experiments/qf_slia_comparison.tex}
  \end{center}
  \caption{Number of solved benchmarks in the set of quantifier-free strings with
    linear integer arithmetic constraints (QF\_SLIA) at SMT-COMP~2023. The numbers are from
    the competition results, except for CA-Str, which is executed by us on the same 
    cluster as the competition with the same resources, and the two virtual portfolio solvers
    \Ostrich+CA and \textsc{Competition} which aggregate the best results from \Ostrich{}/CA-Str and 
    all the competition results for non-\Ostrich{} solvers respectively. }
  \label{tab:solve-status-smt-comp}
\end{table}

@@

We picked QF\_SLIA since
\Ostrich{} already performed well on the other two string solving tracks. In fact,
every solver, including \Ostrich{}, handled every benchmark in QF\_SNIA within the timeout.
%
As can be seen from \cref{tab:solve-status-smt-comp}, integrating \Catra{} as a back-end
leads to gains both on satisfiable and unsatisfiable problems. On
satisfiable problems, the combination \Ostrich+CA is still
outperformed by cvc5 and z3alpha. On unsatisfiable benchmarks,
\Ostrich+CA now narrowly beats the other solvers by squeezing past cvc5,
which is promising given that \Ostrich{}~1.3 (without CA-Str), cvc5, and z3alpha all show very strong
performance on this class of benchmarks. Similar improvements
occur in QF\_S, they are much smaller (an additional 2 unsatisfiable, 4 satisfiable 
solved out of~8\,847 in total).

The results show that \Calculus{} can be used to enhance the performance of an
automaton-based string solver. The results should be considered preliminary,
however, as we believe that a deeper integration of \Catra{} into string solvers
can lead to significant performance gains. In particular, the integration layer 
is currently too shallow to allow \Ostrich{} to learn clauses generated by \Catra{}
and additionally incurs subprocess-spawning overhead and others, as well as overhead
from serialising and deserialising the current Parikh automata problem into \Catra{}'s
input format.

>>>>

\begin{table}
  \begin{center}
  \input{graphs/qf_slia_comparison.tex}
  \end{center}
  \caption{Number of solved benchmarks in the set of quantifier-free strings with
    linear integer arithmetic constraints (QF\_SLIA) at SMT-COMP~2023. The numbers are from
    the competition results, except for CA-Str, which is executed by us on the same 
    cluster as the competition with the same resources, and the two virtual portfolio solvers
    \Ostrich+CA and \textsc{Competition} which aggregate the best results from \Ostrich{}/CA-Str and 
    all the competition results for non-\Ostrich{} solvers respectively. }
  \label{tab:solve-status-smt-comp}
\end{table}

\begin{figure}[t]
  \includegraphics[width=\linewidth]{graphs/smt-comp-cactus}
  \caption{The number of instances solved in the QF\_SLIA track of SMT-COMP 2023
   as the time budget increases towards the competition limit of \numprint{20}~minutes.}
  \label{fig:smt-comp:cactus}
  \Description[A cactus plot comparing the performance of the solvers in the QF_SLIA track of SMT-COMP]%
  {The plot shows the results for the solvers Ostrich 1.3, CA-Str, Ostrich+CA, Z3-Noodler,
  cvc5 and z3alpha as number of solved instances (y-axis) after N seconds (x-axis). The
  topmost solver is the virtual portfolio "Competition", representing every non-Ostrich
  solver, followed by cvc5, after ca 200 seconds, after which it overtakes the previous leader, z3alpha.}
\end{figure}

@@

We picked QF\_SLIA since
\Ostrich{} already performed well on the other two string solving tracks. In fact,
every solver, including \Ostrich{}, handled every benchmark in QF\_SNIA within the timeout.
%
As can be seen from \cref{tab:solve-status-smt-comp} and \cref{fig:smt-comp:cactus},
integrating \Catra{} as a back-end
leads to gains both on satisfiable and unsatisfiable problems. On
satisfiable problems, the combination \Ostrich+CA is still
outperformed by cvc5 and z3alpha. On unsatisfiable benchmarks,
\Ostrich+CA now narrowly beats the other solvers 
(shown as another virtual portfolio solver, "Competitors") by squeezing past cvc5,
which is promising given that \Ostrich{}~1.3 (without CA-Str), cvc5, and z3alpha all show very strong
performance on this class of benchmarks. Similar improvements
occur in QF\_S, they are much smaller (an additional 2 unsatisfiable, 4 satisfiable 
solved out of~8\,847 in total).

The results show that \Calculus{} can be used to enhance the performance of an
automaton-based string solver. Moreover, the cactus plot in \cref{tab:solve-status-smt-comp} 
illustrates that
CA-Str is immediately useful, boosting the results for the \Ostrich{} portfolio
even at the first datapoint. These results should be considered preliminary,
however, as we believe that a deeper integration of \Catra{} into string solvers
can lead to significant performance gains. In particular, the integration layer 
is currently too shallow to allow \Ostrich{} to learn clauses generated by \Catra{}
and additionally incurs subprocess-spawning overhead and others, as well as overhead
from serialising and deserialising the current Parikh automata problem into \Catra{}'s
input format.
